Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-20 paper/ijcai/paper.tex
more updates in S4.1

\noindent
where $C$ is the cost of diagnosis. $C$ is the mean ranking of all buggy statements.
A positive $\Delta$C means that the position of the faulty statement has decreased
in the ranking after applying the \combpar{k} approach. Hence, reducing the cost of
locating the bug. We also assume a perfect bug understanding, i.e., if the developer
sees the bug in the ranking, he can say it is the faulty one.

@@

\subsubsection{RQ1: \textit{How often DS misses faulty statements?}}
\label{sec:fault-misses}

@@

\subsubsection{RQ2: \textit{How effective is the \comb{} combination for bug localization?}}

@@

Table \ref{fig:diagnosis} reports the performance of the diagnosis using \comb{}-5 and \comb{}-10 instead of only using \sfl{}. $\Delta C <0$ means that the faulty statement may be removed. $\Delta C=0$ means that the faulty statement remained in the same position. $\Delta C >0$ means that \ds{} improved diagnosability.

>>>>

\noindent
where $C$ is the cost of diagnosis. $C$ is the mean ranking of all buggy statements.
$\Delta C >0$ means that the position of the faulty statement has decreased
in the ranking after applying the \combpar{k} approach. Hence, reducing the cost of
locating the bug. $\Delta C <0$ means that the 
faulty statement may be removed by \combpar{k}. $\Delta C=0$ means that the faulty statement 
remained in the same position.  We also assume a perfect bug understanding, i.e., if the developer
sees the bug in the ranking, he can say it is the faulty one.

@@

\subsubsection{RQ1: \textit{How often \ds{} misses faulty statements?}}
\label{sec:fault-misses}

@@

\subsubsection{RQ2: \textit{How effective is the \combpar{k} combination for bug localization?}}

@@

Table \ref{fig:diagnosis} reports the performance of the diagnosis using \comb{}-5 and \comb{}-10 instead of only using \sfl{}.
